Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-04-17 paper.qmd
Updated Figure 5 titles

trimesh_two_curvy_removed1_tsne_with_data <- ggplot() +
  geom_point(data = tsne_two_curvy_scaled,
             aes(
               x = tSNE1,
               y = tSNE2
             ),
             color = clr_choice,
             alpha = 0.5,
             size = 0.5) +
  geom_segment(data = tr_from_to_df_two_curvy,
               aes(
                 x = x_from,
                 y = y_from,
                 xend = x_to,
                 yend = y_to),
               colour = "#000000") +
  interior_annotation("a", sc_ltr_pos, cex = 1.5) +
  theme(aspect.ratio = 1)
```

>>>>

trimesh_two_curvy_removed1_tsne_with_data <- ggplot() +
  geom_point(data = tsne_two_curvy_scaled,
             aes(
               x = tSNE1,
               y = tSNE2
             ),
             color = clr_choice,
             alpha = 0.5,
             size = 0.5) +
  geom_segment(data = tr_from_to_df_two_curvy,
               aes(
                 x = x_from,
                 y = y_from,
                 xend = x_to,
                 yend = y_to),
               colour = "#000000") +
  interior_annotation("a", sc_ltr_pos, cex = 1.2) +
  theme(aspect.ratio = 1)
```
